refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-07-25 paper/manuscript.tex
PAPER: some campbell comments

The \Objective\ class uses the \ReflectModel\ and a dataset, \DataD, to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model.
The \DataD\ object has \emph{x, y, y\_err, x\_err} attributes to represent $Q$, $R$, $\mathrm{d}R$, $\mathrm{d}Q$. The \DataD\ object can be constructed from a tuple of arrays representing the data, or by reading a three or four column plain-text datafile. A three column dataset represents $Q$ (\si{\per\angstrom}), $R$, $\mathrm{d}R$ (1 standard deviation). A four column dataset represents $Q$, $R$, $\mathrm{d}R$, $\mathrm{d}Q$ (\si{\per\angstrom}). Subclassing \DataD\ would allow other formats to be read. One example of this could be an wavelength dispersive file using $\Omega$, $\lambda$ data instead of $Q$; such as that used in energy scanned X-ray reflectometry, or sometimes produced by wavelength dispersive neutron reflectometers. In such a case \ReflectModel\ could be subclassed to make full use of this energy dispersive information.
An \Objective\ can be given a \Transform\ object to permit fitting as $\log R$ vs $Q$, $RQ^4$ vs $Q$, or $R$ vs $Q$. Several \Objective\ can be combined to form a \GlobalObjective\ for co-refinement. The object-oriented nature allows \Parameter\, \Component\ to be reused in in different \Objective, thereby facilitating co-refinement.
%FIXME: above said 'lin-R' is that linear or natural log (\ln)

@@

%TODO add (a) and (b)
\caption{a) Reflectivity from a DMPC bilayer measured at three contrasts, with 500 samples from the posterior distribution in grey and median of the distribution in red. Data for \ce{Si} match and \ce{H_2O} contrast offset by 0.1 and 0.001 respectively. b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median in red. It is seen that the uncertainty in the reflectivity at high $Q$ is associated with an uncertainty in SLD profile at the lipid-\ce{D2O} interface.}
\end{figure}

@@

In order for a given scattering analysis to be fully reproducible by others, a general set of conditions need to be met:
\begin{itemize}
  \item the datasets used need to be deposited with a journal article, or be freely available.
  %FIXME is that the raw data or the reduced data?
  \item the exact software environment needs to be recreatable.
  %FIXME refnx does not address this further down the stack
  \item the exact ordered set of steps taken during the analysis needs to be listed.
\end{itemize} 
Each of these points are often omitted in the literature. For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may preclude recording the full set of steps, or options, applied by a user. Whilst it is unable to meet the first criteria by itself, the use of \refnx\ in a \Jupyter\ notebook can fulfil the other two requirements, providing a little care is taken. As we have already notes, the ordered set of steps to perform the analysis is the \Jupyter\ notebook in which the analysis was performed and this is an artefact able to be archived.

>>>>

The \Objective\ class uses the \ReflectModel\ and a dataset, \DataD, to calculate $\chi^2$, log-likelihood, log-prior, residuals, and the generative model.
The \DataD\ object has \emph{x, y, y\_err, x\_err} attributes to represent $Q$, $R$, $\mathrm{d}R$, $\mathrm{d}Q$. The \DataD\ object can be constructed from a tuple of arrays representing the data, or by reading a three or four column plain-text datafile. A three column dataset represents $Q$ (\si{\per\angstrom}), $R$, $\mathrm{d}R$ (1 standard deviation). A four column dataset represents $Q$, $R$, $\mathrm{d}R$, $\mathrm{d}Q$ (\si{\per\angstrom}). Subclassing \DataD\ would allow other formats to be read. One example of this could be an wavelength dispersive file using $\Omega$, $\lambda$ data instead of $Q$; such as that used in energy scanned X-ray reflectometry, or sometimes produced by wavelength dispersive neutron reflectometers. In such a case \ReflectModel\ could be subclassed to make full use of this energy dispersive information.
An \Objective\ can be given a \Transform\ object to permit fitting as $\log_{10} R$ vs $Q$, $RQ^4$ vs $Q$; the default (no \Transform) is $R$ vs $Q$. Several \Objective\ can be combined to form a \GlobalObjective\ for co-refinement. The object-oriented nature allows \Parameter\, \Component\ to be reused in in different \Objective, thereby facilitating co-refinement.

@@

%TODO add (a) and (b)
\caption{a) Neutron reflectivity from a DMPC bilayer supported on a silicon crystalmeasured at three contrasts, with 500 samples from the posterior distribution in grey and median of the distribution in red. Data for the hdmix and \ce{H_2O} contrast offset by 0.1 and 0.001 respectively. b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median in red. It is seen that the uncertainty in the reflectivity at high $Q$ is associated with an uncertainty in SLD profile at the lipid-\ce{D2O} interface.}
\end{figure}

@@

In order for a given scattering analysis to be fully reproducible by others, a general set of conditions need to be met:
\begin{itemize}
  \item the datasets used need to be deposited with a journal article, or be freely available.
  %FIXME is that the raw data or the reduced data?
  \item the exact software environment needs to be recreatable.
  %FIXME refnx does not address this further down the stack
  \item the exact ordered set of steps taken during the analysis needs to be listed.
\end{itemize} 
Each of these points are often omitted in the literature. For example, the use of different software versions may change the output of an analysis, or the use of a GUI program may preclude recording the full set of steps, or options, applied by a user. Whilst it is unable to meet the first criterion by itself, the use of \refnx\ in a \Jupyter\ notebook can fulfil the other two requirements, providing a little care is taken. As we have already notes, the ordered set of steps to perform the analysis is the \Jupyter\ notebook in which the analysis was performed and this is an artefact able to be archived.
